---
title: "Dec-16 IQC Report"
author: "Pierre Baudin"
date: "January 12, 2017"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Incoming Quality Report - December 2016

### December Dataset

Data are provided from the daily recording of incoming batch issues.

```{r IQCdataimport, message=FALSE, warning=FALSE, include=FALSE}
library(purrr)
library(dplyr)
library(lubridate)
library(readxl)

# Test directory
setwd("D:/Data Science/QAS_R_Project/IQC Monitoring")

filename <- "IQC_defect_table_update.xlsx"

#Import sheet 1
IQC_df <- read_excel(filename, col_types = c("date", "text", "text", "text", "text", "text",
                                          "text", "text", "text", "text", "numeric", "text",
                                          "text","text", "text", "text", "numeric", "numeric",
                                          "text"))
#check dimension of IQC_df
dim_IQC_df <- dim(IQC_df) ;
#remove last row from excel table (calculation row from excel)
IQC_df <- as.data.frame(IQC_df[-(dim_IQC_df[1] - 1), ])

# Clean data as factor
c_names <- names(IQC_df)
colfact <- c_names[c(2, 3, 4, 5, 6, 7, 8, 9, 10, 12, 13, 14, 15, 16, 19)]
IQC_df[ , colfact] <- map(IQC_df[ , colfact], factor)
#Convert Date into Year - Month - Day
IQC_df$Date <- ymd(IQC_df$Date)

#Rename column
IQC_df <- rename(IQC_df, DocNum = `SAP PO / MO no.`);
IQC_df <- rename(IQC_df, ItemCode = `Part number`);
IQC_df <- rename(IQC_df, IssueCat = `Issue cat.`);
IQC_df <- rename(IQC_df, CardCode = Supplier);

## Import Supplier list
filename <- "Supplierlistcc.xlsx"

Supplier <- read_excel(filename, col_types = c("text", "text"))
Supplier$CardCode <- as.factor(Supplier$CardCode)

## Join IQC_df and Supplier list
IQC_df <- left_join(IQC_df, Supplier, by = "CardCode")

## December results
IQC_Dec <- IQC_df %>%
      filter(Date >= "2016-12-01" & Date <= "2016-12-31")

```


The following table summarizes the number of lots accepted, accepted with deviation and rejected.

Note: Lot accepted are listed in the monitoring table as the QC team found an issue such as missing PPAP or PI for example.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
table(IQC_Dec$Result)
```


### Calculation details

#### Result Weight

To help with the calculation, the outcome of an inspection has been given a weight as follow:

```{r, echo=FALSE, message=FALSE, warning=FALSE}
Weight <- data.frame(Result = c("Accepted", "Deviation", "Rejected"), Weight = c(2, 4, 8))
Weight
```

#### Category and Weight

A list of the issue category is available below. Each category has been assigned a weight to support calculation in the next section.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
CatWeight <- data.frame( IssueCat = c("Appearance", "Construction",
                                      "Dimension", "Engineering",
                                      "Function", "Marking", "Material", "Packaging",
                                      "PPAP", "PI"),
                         CatWeight = c(2, 5, 3, 1, 5, 3, 3, 2, 1, 1))
CatWeight
```

### Computation of the Top 15 supplier by number of Occurence 

```{r, message=FALSE, warning=FALSE, include=FALSE}
# Combine dataset with Result weight
IQC_Dec <- left_join(IQC_Dec, Weight, by = "Result")

# Combine dataset with category weigth
IQC_Dec <- left_join(IQC_Dec, CatWeight, by = "IssueCat")

TallyDec16 <- IQC_Dec %>% 
      mutate(Ratio = Severity * Weight * CatWeight) %>%
      group_by(CardCode, Result, Ratio) %>%
      tally() %>%
      ungroup()

Top15Dec_Occurence <- TallyDec16 %>%
      arrange(desc(n), desc(Ratio)) %>%
      head(n = 15)

Top15Dec_Ratio <- TallyDec16 %>%
      arrange(desc(Ratio), desc(n)) %>%
      head(n = 15)

```

Count of issue occurence in December 2016 results in the following table. Only the Top 15 suppliers are listed.

```{r, echo=FALSE}
Top15Dec_Occurence
```


### Computation of the Top 15 supplier usign quality ratio

The quality ratio is calculated as follow:

**Ratio = Result Weight x Severity x Category Weight**

*Note:*  
*In the future, this ratio can be adjusted using the price, quantity and other factors related to the material.*

The following table output the Top 15 suppliers that had the highest quality defect ratio:

```{r, echo=FALSE}
Top15Dec_Ratio
```

## Final list of suppliers

The final list of suppliers combine the suppliers with the highest occurence and highest quality ratio.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# compute teh intersection of the 2 calculated top 15
TopSup <- intersect(Top15Dec_Occurence$CardCode, Top15Dec_Ratio$CardCode)
TopSup <- as.data.frame(TopSup)
left_join(TopSup, Supplier, by = c("TopSup" = "CardCode"))
```
